Validating FF-Replan vs.\@ a State-Of-The-Art Probabilistic Planner in Translated Real World Domains

### 2014-03-30 FinalPaper/paper.tex
describing domain

Since the first incorporation of the International Probabilistic Planning
Competition (IPPC), it has undergone radical changes. Dominating planners
of previous incorporations had a strong focus on goal-oriented MDPs,
determinizing and using powerful classical planners (e.g. FF
\cite{Hoffmann01theff}) and replanning. New benchmarks have demonstrated
weaknesses in existing solution techniques.

Little and Thi\'ebaux have developed a baseline test in
\cite{little2007probvsreplan} to evaluate the IPC-5 problems. This
test determines if a planning problem is `probabilistically interesting'.
Problems that fail this test are classical planning problems in disguise.
Knowing this it is easy to design a problem where a replanner performs badly
or incredibly well.

The IPPC-11 introduced Relation Dynamic Influence Diagram Language (RDDL),
which can design domains that are more probabilistically interesting. The top
performers were PROST \cite{keller2012prost} and Glutton
\cite{kolobov2012glutton}.

While it is interesting to make problems harder and invent better planning
algorithms to solve those probabilistic complex problems, one must not forget
if the problem makes sense in the real world.

The main contribution of this paper is an evaluation of the domains used in
IPPC-11 and see if they can be adjusted so they fail the baseline test for
probabilistic interestingness, which might make them more suitable for
replanning planners.

@@

\section{Domain Descriptions}

\subsection{IPPC-2011 Domains}

>>>>

The baseline test in \cite{little2007probvsreplan} evaluates the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners. We would like to carefully analyze the credibility of these domains in the real world and evaluate the worth of FF-Replan vs a state of the art probabilistic planner: Gourmand \cite{kolobov2012gourmand}.

@@

\subsection{Gourmand}
The IPPC-2011 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy. For this reason planners needed to be scalable and sensitive to the expected reward maximization. Glutton introduces an off-line algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a successful policy can be produced by solving an MDP $M(H)$ for a smaller horizon $h$. Incrementally solving the sequence $M(1)$, $M(2)$ forms the basis of LR\textsuperscript{2}TDP\@. By iterating on the distance from the horizon, data can be reused (and is stored in the cache until the hash-table is full). The max-reward heuristic finds the largest horizon value $h'$ for which already a heuristic value $V$ is estimated. The  computation time remains much lower because it runs quickly into states that converged while solving $M(h-1)$. The max-reward computation relies on knowing the maximum $R_{max}$ any action can yield in any state or an upper bound on it.

During IPPC-2011 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT. This caused to wonder whether LRTDP planners could outperform UCT based systems.  UCT forces an expert to guess a non-shortsighted lookahead value for which it should be able to converge on encountered states. Choosing this value can have very bad consequences and its existence causes the UCT to require some input, taking away from its autonomicity. At the IPPC-2011 GLUTTON was an offline LRTDP based planner that came second. As PROST employed UCT in an online manner, GOURMAND is an online adaptation of the GLUTTON algorithm to test whether LRTDP performs better if it is employed online.

\section{Domain Descriptions}
Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed. Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}. This section describes interesting domains in which either FF-Replan or Gourmand prevailed during the International Probabilistic Planning Compeitions. These domains are evaluated for how well they portray real-world scenarios. The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario. Little et all's baseline test helps us to predict which planner would perform well on these domains. We will then conclude our evaluation by comparing these results to the result of our experiments described in Section \ref{sec:experiment}.

\subsection{IPPC-2011 Domains}
The competitor FF-Replan \cite{FFReplan} kindly remembered the committee of the IPPC-04 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty. The baseline test of Little et. all evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners. IPPC-2011 responded by introducing more realistic MDPs and evluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.

GOURMAND vastly outperformed IPPC-11 UCT-based probabilistic track winner PROST by far on goal-oriented domains Navigation and Crossing Traffic \cite{kolobov2012gourmand}. Prost however midly outperforms GOURMAND on the Game of Life, Sysadmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.

\subsubsection{Navigation domain}
The navigation domain represents a grid in which a robot must reach a goal. Every cell offers the robot a different chance of dissapearinng. The robot needs to choose a path which gets it to the goal most reliably within the finite horizon time \cite{sanner2011navigation}. Because GOURMAND uses a dynamic lookahead, it performs quite well in this domain.

%ADD IMAGE HERE

\subsubsection{Traffic domain}
This domain represents a simple binary version of the cell transition model (CTM) for modelling traffic based on the original CTM Tech Report \cite{sanner2011traffic}. Because of the binary variables and no intermediate variable restrictions, this model is simplified and ignores traffic aspects such as turns and turn probabilities. This model also uses concurrent actions and the total actions has an upperbound of 2\^ (\# of intersections).

\subsection{IPPC-04 Domains}
Duing IPPC-04, the domains were written in the Probabilistic PLanning Domain Description Language (PPDDL). 30 trials per problem were to be solved in 15 minutes.

\subsubsection{}

\subsubsection{}
